Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2023-02-10 write-up/fda-recurrent.tex
updated related work and added contributions and outline

\usepackage{soul,color, mathtools, fixmath}
\usepackage{multirow}
\usepackage[shortlabels]{enumitem}
\def\pr{\mathop{\text{pr}}\nolimits}
\def\var{\mathop{\text{var}}\nolimits}
\def\cov{\mathop{\text{cov}}\nolimits}
\def\k{{\bf k}}
\def\z{{\bf z}}
\def\W{{\bf W}}
\def\Bka{{\it Biometrika}}
\def\AIC{\textsc{aic}}
\def\T{{ \mathrm{\scriptscriptstyle T} }}
\def\v{{\varepsilon}}
\def\partitionsn{\mathop{\mathcal{P}_{[n]}}\nolimits}
\def\partitionsN{\mathop{\mathcal{P}_{\infty}}\nolimits}
\def\Dmn{\mathop{{D}_{m,n}}\nolimits}
\def\symmetricn{\mathop{\mathcal{S}_{n}}\nolimits}
\def\PE{\mathop{\rm Pitman\mbox{-}Ewens}\nolimits}
\def\per{\mathop{\rm per}\nolimits}
\def\U{\mathop{\mathcal{U}_{}}\nolimits}
\def\Nb{\mathop{\mathbb{N}_{}}\nolimits}
\def\Nbb{\mathop{\mathbf{N}_{}}\nolimits}
\def\nbb{\mathop{\mathbf{n}_{}}\nolimits}
\def\Xbb{\mathop{\mathbf{X}_{}}\nolimits}
\def\fin{\mathop{\text{fin}}\nolimits}
\def\pr{\mathop{\text{pr}}\nolimits}
\def\E{\mathcal{E}}
\def\G{\mathcal{G}}
\def\deg{\text{deg}_{}}
\def\equalinlaw{=_{\mathcal{D}}}
\def\Fk{\mathop{\mathcal{F}_k^{\downarrow}}\nolimits}
\def\F{\mathop{\mathcal{F}^{\downarrow}}\nolimits}
\def\size{\mathop{\text{size}}\nolimits}
\def\Ycong{\mathop{\EY}\nolimits}
\def\EIsig{\mathop{\mathcal{E}_{\mathcal{I}}^{\sigma}}\nolimits}
\def\EY{\mathop{\mathcal{E}_{Y}}\nolimits}
\def\finp{\mathop{\fin(\mathcal{P})}\nolimits}
\def\En{\mathop{\mathfrak{E}_{[n]}}\nolimits}
\def\EN{\mathop{\mathfrak{E}_{\Nb}}\nolimits}
\def\logit{\mathop{\text{logit}_{}}\nolimits}
\def\EI{\mathop{\mathcal{E}_{\mathcal{I}}}\nolimits}
\def\ES{\mathop{\mathfrak{E}_S}\nolimits}
\def\Ifk{\mathop{{I}_{}}\nolimits}
%\def\mathcal{I}{\mathop{\mathcal{I}_{}}\nolimits}
\def\Ycong{\mathop{\EY}\nolimits}
\def\EIsig{\mathop{\mathcal{E}_{\mathcal{I}}^{\sigma}}\nolimits}
\def\EY{\mathop{\mathcal{E}_{Y}}\nolimits}
\def\finp{\mathop{\fin(\mathcal{P})}\nolimits}
\def\En{\mathop{\mathfrak{E}_{[n]}}\nolimits}
\def\EN{\mathop{\mathfrak{E}_{\Nb}}\nolimits}
\def\logit{\mathop{\text{logit}_{}}\nolimits}
\def\EI{\mathop{\mathcal{E}_{\mathcal{I}}}\nolimits}
\def\ES{\mathop{\mathfrak{E}_S}\nolimits}
\DeclareRobustCommand{\citeext}[1]{\citeauthor{#1} (\citeyear{#1})}
\DeclareRobustCommand{\citeint}[1]{(\citeauthor{#1}, \citeyear{#1})}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{defn}[thm]{Definition}
\newtheorem{example}[thm]{Example}
\newtheorem{meas}[thm]{Measurement}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{assumption}[thm]{Assumption}
\newtheorem{rmk}[thm]{Remark}%\endlocaldefs
% change default numbering for enumerate environment to be in parentheses
\makeatletter
\def\S{\mathcal{S}}
\def\indep{\mathrel{\rlap{$\perp$}\kern1.6pt\mathord{\perp}}}
\def\R{\mathcal{R}}
\def\H{\mathcal{H}}
\def\E{\mathbb{E}}
\def\Y{{\bf Y}}
\def\Cov{\text{Cov}}
\def\one{{\bf 1}}
\def\diag{\text{diag}}
\def\given{\, | \,}
\def\Given{\, \big | \,}
\def\Nat{\mathbb{N}}
\def\Real{\mathbb{R}}
\def\bft{{\bf t}}
\def\bfx{{\bf x}}
\def\bfp{{\bf p}}
\def\bfT{{\bf T}}
\def\bfD{{\bf D}}
\def\dotminussym#1#2{%
  \setbox0=\hbox{$\m@th#1-$}%
  \kern.5\wd0%
  \hbox to 0pt{\hss\hbox{$\m@th#1-$}\hss}%
  \raise.6\ht0\hbox to 0pt{\hss$\m@th#1.$\hss}%
  \kern.5\wd0}
\newcommand{\dotminus}{\mathbin{\mathpalette\dotminussym{}}}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\mathchardef\mhyphen="2D
% display breaks

@@

\section{Recurrent event process and associated high frequency data}

@@

\section{Longitudinal functional principal components within
  event-history analysis}

Probabilistic subsampling converts the single sensor stream~$\bfx_i$ into a sequence of functions observed repeatedly at sampled times~$\bfD_i$ and event times~$\bfT_i$ over windows of length~$\Delta$. Such a data structure is commonly referred to as \emph{longitudinal functional data}~\citep{Xiao2013, GoldSmith2015}. Given the large increase in longitudinal functional data in recent years, corresponding analysis has received much recent attention~\citep{Morris2003, MorrisCarroll2006, Baladandayuthapani2008, Di2009, Greven2010, Staicu2010, ChenMuller2012, LiGuan2014}. Here, we combine work by~\cite{Park2018} and~\cite{Goldsmith2011} to construct a computationally efficient penalized functional method for solving the estimation equations~$\hat U_n (\theta)$.

@@

The next step of our method is modeling~$\beta(s)$. Here, we leverage ideas from the penalized spline literature~\citep{Ruppert2003, Wood2006book}. Let~$\mathbold{\phi} (s) = \{ \phi_1 (s), \ldots, \phi_{K_b} (x) \}$ be a spline basis and assume that~$\beta(s) = \sum_{j=1}^{K_b} b_j \phi_{j} (s) = \mathbold{\phi} (t) {\bf b}$ where~${\bf b} = [b_1, \ldots, b_{K_b}]^{\top}$. Thus, the integral in~\eqref{eq:hazardlinear} can be restated as
\begin{align*}
\int_{t-\Delta}^t X(t,s) \beta(s) ds
  &\approx \int_{t-\Delta}^t \left[ \hat \mu(t,s) + {\bf c} (t)^\top
    \mathbold{\hat \psi} (s) \right] \times \left[
    \mathbold{\phi} (s) {\bf b} \right] ds \\
  &= [ M_{i,t}^\top + {\bf c} (t)^\top J_{\hat \psi, \phi} ] {\bf b}
\end{align*}
where~$M_{t} = (M_{1,t}, \ldots, M_{K_b,t})$, $M_{j,t} = \int_{t-\Delta}^t \hat \mu (t,s) \phi_j (s)$, and~$J_{\hat \psi, \phi}$ is a $K_x \times K_b$ dimensional matrix with the~$(k,l)$th entry is equal to~$\int_{0}^\Delta \hat \psi_k (s) \phi_l (s) ds$~\citep{RamsaySilverman2005}.

@@

\subsection{Theoretical analysis}

@@

\subsection{Computation versus statistical efficiency tradeoff}

@@

We acknowledge two important limitations of confidence intervals obtained via this approach. First, penalization may lead to confidence intervals that perform poorly in regions where~$\hat \beta(t)$ is oversmoothed. Second, we ignore the variability inherent in the longitudinal functional principal component analysis; that is, our estimates ignore the variability in estimation of eigenfunctions~$\hat \psi$ as well as the coefficients~$\hat c_{i,k}(t)$. Joint modeling could be considered as in~\cite{Crainiceanu2010}, however, this is beyond the scope of this article.

@@

\subsection{Comparison to alternative methods} \label{section:simcomparisons}

\section{Extensions}

@@

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/smoothed_eda.png}
  \caption{Electrodermal activity (EDA)}
  \label{fig:mean_eda}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/smoothed_ai.png}
  \caption{Activity Index (AI)
}  \label{fig:mean_acc}
\end{subfigure}
\caption{Average scaled EDA and AI in the 30 minutes prior to button presses}
\label{fig:mean_edacc}
\end{figure}

@@

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/eda_coef_joint.png}
  \caption{Electrodermal activity (EDA)}
  \label{fig:eda_estimate}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/acc_coef_joint.png}
  \caption{Activity Index (AI)
}  \label{fig:acc_estimate}
\end{subfigure}
\caption{$\beta (t)$ for ACC and EDA with 95\% CI; solid line is point estimate for the complete-case analysis, while highlighted region are the model-based pointwise 95\% confidence intervals.}
\label{fig:mean_edacc}
\end{figure}

@@

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/eda_coef_joint_bootstrap.png}
  \caption{Electrodermal activity (EDA)}
  \label{fig:eda_estimate_bs}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/acc_coef_joint_bootstrap.png}
  \caption{Activity Index (AI)
}  \label{fig:acc_estimate_bs}
\end{subfigure}
\caption{$\beta (t)$ for ACC and EDA with 95\% CI; solid line is point estimate for the missing data analysis, while highlighted region are the boostrap and MI based pointwise 95\% confidence intervals.}
\label{fig:mean_edacc}
\end{figure}

>>>>

\usepackage{soul,color, mathtools, fixmath}
\usepackage{multirow}
\usepackage[shortlabels]{enumitem}
\def\pr{\mathop{\text{pr}}\nolimits}
\def\var{\mathop{\text{var}}\nolimits}
\def\cov{\mathop{\text{cov}}\nolimits}
\def\k{{\bf k}}
\def\z{{\bf z}}
\def\W{{\bf W}}
\def\Bka{{\it Biometrika}}
\def\AIC{\textsc{aic}}
\def\T{{ \mathrm{\scriptscriptstyle T} }}
\def\v{{\varepsilon}}
\def\partitionsn{\mathop{\mathcal{P}_{[n]}}\nolimits}
\def\partitionsN{\mathop{\mathcal{P}_{\infty}}\nolimits}
\def\Dmn{\mathop{{D}_{m,n}}\nolimits}
\def\symmetricn{\mathop{\mathcal{S}_{n}}\nolimits}
\def\PE{\mathop{\rm Pitman\mbox{-}Ewens}\nolimits}
\def\per{\mathop{\rm per}\nolimits}
\def\U{\mathop{\mathcal{U}_{}}\nolimits}
\def\Nb{\mathop{\mathbb{N}_{}}\nolimits}
\def\Nbb{\mathop{\mathbf{N}_{}}\nolimits}
\def\nbb{\mathop{\mathbf{n}_{}}\nolimits}
\def\Xbb{\mathop{\mathbf{X}_{}}\nolimits}
\def\fin{\mathop{\text{fin}}\nolimits}
\def\pr{\mathop{\text{pr}}\nolimits}
\def\E{\mathcal{E}}
\def\G{\mathcal{G}}
\def\deg{\text{deg}_{}}
\def\equalinlaw{=_{\mathcal{D}}}
\def\Fk{\mathop{\mathcal{F}_k^{\downarrow}}\nolimits}
\def\F{\mathop{\mathcal{F}^{\downarrow}}\nolimits}
\def\size{\mathop{\text{size}}\nolimits}
\def\Ycong{\mathop{\EY}\nolimits}
\def\EIsig{\mathop{\mathcal{E}_{\mathcal{I}}^{\sigma}}\nolimits}
\def\EY{\mathop{\mathcal{E}_{Y}}\nolimits}
\def\finp{\mathop{\fin(\mathcal{P})}\nolimits}
\def\En{\mathop{\mathfrak{E}_{[n]}}\nolimits}
\def\EN{\mathop{\mathfrak{E}_{\Nb}}\nolimits}
\def\logit{\mathop{\text{logit}_{}}\nolimits}
\def\EI{\mathop{\mathcal{E}_{\mathcal{I}}}\nolimits}
\def\ES{\mathop{\mathfrak{E}_S}\nolimits}
\def\Ifk{\mathop{{I}_{}}\nolimits}
%\def\mathcal{I}{\mathop{\mathcal{I}_{}}\nolimits}
\def\Ycong{\mathop{\EY}\nolimits}
\def\EIsig{\mathop{\mathcal{E}_{\mathcal{I}}^{\sigma}}\nolimits}
\def\EY{\mathop{\mathcal{E}_{Y}}\nolimits}
\def\finp{\mathop{\fin(\mathcal{P})}\nolimits}
\def\En{\mathop{\mathfrak{E}_{[n]}}\nolimits}
\def\EN{\mathop{\mathfrak{E}_{\Nb}}\nolimits}
\def\logit{\mathop{\text{logit}_{}}\nolimits}
\def\EI{\mathop{\mathcal{E}_{\mathcal{I}}}\nolimits}
\def\ES{\mathop{\mathfrak{E}_S}\nolimits}
\DeclareRobustCommand{\citeext}[1]{\citeauthor{#1} (\citeyear{#1})}
\DeclareRobustCommand{\citeint}[1]{(\citeauthor{#1}, \citeyear{#1})}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{defn}[thm]{Definition}
\newtheorem{example}[thm]{Example}
\newtheorem{meas}[thm]{Measurement}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{assumption}[thm]{Assumption}
\newtheorem{rmk}[thm]{Remark}%\endlocaldefs
% change default numbering for enumerate environment to be in parentheses
\makeatletter
\def\S{\mathcal{S}}
\def\indep{\mathrel{\rlap{$\perp$}\kern1.6pt\mathord{\perp}}}
\def\R{\mathcal{R}}
\def\H{\mathcal{H}}
\def\E{\mathbb{E}}
\def\Y{{\bf Y}}
\def\Cov{\text{Cov}}
\def\one{{\bf 1}}
\def\diag{\text{diag}}
\def\given{\, | \,}
\def\Given{\, \big | \,}
\def\Nat{\mathbb{N}}
\def\Real{\mathbb{R}}
\def\bft{{\bf t}}
\def\bfx{{\bf x}}
\def\bfp{{\bf p}}
\def\bfT{{\bf T}}
\def\bfD{{\bf D}}
\def\dotminussym#1#2{%
  \setbox0=\hbox{$\m@th#1-$}%
  \kern.5\wd0%
  \hbox to 0pt{\hss\hbox{$\m@th#1-$}\hss}%
  \raise.6\ht0\hbox to 0pt{\hss$\m@th#1.$\hss}%
  \kern.5\wd0}
\newcommand{\dotminus}{\mathbin{\mathpalette\dotminussym{}}}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\mathchardef\mhyphen="2D
% display breaks
\newenvironment{newmaterial}{\par\color{blue}}{\par}

@@

\begin{newmaterial}
The use of smart devices and other wearables to passively monitor patients has led to a rapid increase in the number of studies with high-frequency sensor streams that can be conceptualized as studies measurements are functions.
The development of such applications have been accompanied by intense methodological development in regression models with functional covariates~\citep{James2002,JamesSilverman2005,muller2005,Ramsay2005,kokoszka2017,doi:10.1198/jasa.2009.tm08564,doi:10.1198/016214507000000527}.

Recently, modelling time-to-event data with functional covariates has received a fair bit of attention.  The functional linear Cox regression model (FLCRM) considers the association between a time-to-event and a set of functional~$\{ X(s) \}$ and scalar predictors~$Z \in \mathbb{R}^p$~\citep{https://doi.org/10.1111/biom.12748}. In this setting, the functional and scalar predictors are observed at baseline and the hazard function satisfies the proportional hazards assumption and involves a non-parametric baseline hazard with the exponential adjustment including both a functional linear model~$\int_S X(s) \beta(s)ds$ and a linear model for the baseline scalar predictors~$Z^\top \gamma$.
Since the linear assumption may be too restrictive,~\cite{doi:10.1080/10618600.2020.1853550} consider a more flexible additive functional Cox model for multivariate functional predictors in which the hazard depends on $\int  F \{s, h_{is}[X_i (s)]\} ds$ where $F$ is an unspecified bivariate twice differentiable function.

In our setting, the high frequency sensor process is an outcome and must therefore be jointly modelled with the recurrent event process.  Recently, \cite{Li2022} proposed a functional approach to joint modelling of multivariate longitudinal biomarkers and a time-to-event outcome~\cite{Tsiatis2004,Rizopoulos2010}.  Here, as in traditional joint models, the longitudinal biomarker is observed at only a few observation times (typically on the order of tens of observations) and is modelled via a functional principal components analysis.  The eigenscores are the shared parameters across the longitudinal and survival submodels.  A similar joint model was proposed in~\cite{Dong2021}.  Inference proceeds by Monte Carlo EM which can require very large Monte Carlo sample size to ensure good performance, and na{\"i}ve implementation may not recover EM's ascent property~\cite{Caffo2005}.

In this paper, we also consider joint modelling of recurrent events and a high frequency sensor process. In contrast to traditional longitudinal biomarkers, sensor processes are observed multiple times per second leading to thousand and/or millions of observations per individual rather.  To address this increase in scale, a design-based perspective is taken in which we subsample non-event times to avoid some of the computationally demanding aspects of joint models.  Subsampling in the context of functional data analysis for massive data has recently been investigated~\citep{https://doi.org/10.48550/arxiv.2104.03446} in which a functional L-optimality criterion is derived. Subsampling is different in our current context, as our goal is to subsample from the individual sensor processes to produce a design-unbiased estimate of the cumulative hazard function.  Finally, traditional joint modeling often consider the hazard function to depend on the current or cumulative value of the health process~\citep{Li2022,Rizopoulos2010}. For high frequency sensor processes, we expect the hazard function to only depend on the recent sensor history; to do so, we use recent history functional linear models~\cite{KIM20111554}.  We combine these models with advances in longitudinal functional data analysis~\citep{Staicu2010} and penalized functional regression~\citep{Goldsmith2015} to perform scalable inference using off-the-shelf software.

\section{Main contributions and outline}

The original contributions of this paper are three-fold.  In Section~\ref{section:modeloverview}, we define our joint model using historical functional linear models, and demonstrate how techniques from design-based inference can be used to circumvent computational challenges of joint modelling.
In Section~\ref{section:longfpc}, we discuss longitudinal functional principal components analysis and demonstrate in Lemma~\ref{lemma:logistic} that the resulting approximate score equations are equivalent to score functions for logistic regression with binary response and an offset related to the subsampling rate meaning our proposed approach can be fit using off-the-shelf software.  An asymptotic analysis is presented in Section~\ref{section:theory}, with an accompanying discussion of the novel computational versus statistical efficiency tradeoff in Section~\ref{section:tradeoff}.   Section~\ref{section:simstudy} presents a simulation study to demonstrate the impact of subsampling rates, the window length parameter, and a computational comparison to existing methods.  Section~\ref{eq:jm} presents a multivariate extension as well as a method to handle missing data.  We end by illustrating our approach using data from a digital monitoring study of suicidal ideation in Section~\ref{section:example}.

\end{newmaterial}

\section{Recurrent event process and associated high frequency data}
\label{section:modeloverview}

@@

\section{Longitudinal functional principal components within
  event-history analysis}
  \label{section:longfpc}

Probabilistic subsampling converts the single sensor stream~$\bfx_i$ into a sequence of functions observed repeatedly at sampled times~$\bfD_i$ and event times~$\bfT_i$ over windows of length~$\Delta$. Such a data structure is commonly referred to as \emph{longitudinal functional data}~\citep{Xiao2013,Goldsmith2015}. Given the large increase in longitudinal functional data in recent years, corresponding analysis has received much recent attention~\citep{Morris2003, MorrisCarroll2006, Baladandayuthapani2008, Di2009, Greven2010, Staicu2010, ChenMuller2012, LiGuan2014}. Here, we combine work by~\cite{Park2018} and~\cite{Goldsmith2011} to construct a computationally efficient penalized functional method for solving the estimation equations~$\hat U_n (\theta)$.

@@

The next step of our method is modelling~$\beta(s)$. Here, we leverage ideas from the penalized spline literature~\citep{Ruppert2003, Wood2006book}. Let~$\mathbold{\phi} (s) = \{ \phi_1 (s), \ldots, \phi_{K_b} (x) \}$ be a spline basis and assume that~$\beta(s) = \sum_{j=1}^{K_b} b_j \phi_{j} (s) = \mathbold{\phi} (t) {\bf b}$ where~${\bf b} = [b_1, \ldots, b_{K_b}]^{\top}$. Thus, the integral in~\eqref{eq:hazardlinear} can be restated as
\begin{align*}
\int_{t-\Delta}^t X(t,s) \beta(s) ds
  &\approx \int_{t-\Delta}^t \left[ \hat \mu(t,s) + {\bf c} (t)^\top
    \mathbold{\hat \psi} (s) \right] \times \left[
    \mathbold{\phi} (s) {\bf b} \right] ds \\
  &= [ M_{i,t}^\top + {\bf c} (t)^\top J_{\hat \psi, \phi} ] {\bf b}
\end{align*}
where~$M_{t} = (M_{1,t}, \ldots, M_{K_b,t})$, $M_{j,t} = \int_{t-\Delta}^t \hat \mu (t,s) \phi_j (s)$, and~$J_{\hat \psi, \phi}$ is a $K_x \times K_b$ dimensional matrix with the~$(k,l)$th entry is equal to~$\int_{0}^\Delta \hat \psi_k (s) \phi_l (s) ds$~\citep{RamsaySilverman2005}.

@@

\subsection{Theoretical analysis}
\label{section:theory}

@@

\subsection{Computation versus statistical efficiency tradeoff}
\label{section:tradeoff}

@@

We acknowledge two important limitations of confidence intervals obtained via this approach. First, penalization may lead to confidence intervals that perform poorly in regions where~$\hat \beta(t)$ is oversmoothed. Second, we ignore the variability inherent in the longitudinal functional principal component analysis; that is, our estimates ignore the variability in estimation of eigenfunctions~$\hat \psi$ as well as the coefficients~$\hat c_{i,k}(t)$. Joint modelling could be considered as in~\cite{Crainiceanu2010}, however, this is beyond the scope of this article.

@@

\subsection{Computational comparison to alternative methods} \label{section:simcomparisons}

\section{Extensions}
\label{section:extensions}

@@

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/smoothed_eda.png}
  \caption{Electrodermal activity (EDA)}
  \label{fig:mean_eda}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/smoothed_ai.png}
  \caption{Activity Index (AI)
}  \label{fig:mean_acc}
\end{subfigure}
\caption{Average scaled EDA and AI in the 30 minutes prior to button presses}
\label{Reduced Rank Mixed Effects Models for Spatially Correlated Hierarchical Functional Data
}
\label{fig:mean_edacc}
\end{figure}

@@

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/eda_coef_joint.png}
  \caption{Electrodermal activity (EDA)}
  \label{fig:eda_estimate}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/acc_coef_joint.png}
  \caption{Activity Index (AI)
}  \label{fig:acc_estimate}
\end{subfigure}
\caption{$\beta (t)$ for ACC and EDA with 95\% CI; solid line is point estimate for the complete-case analysis, while highlighted region are the model-based pointwise 95\% confidence intervals.}
\label{fig:edacc_estimate}
\end{figure}

@@

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/eda_coef_joint_bootstrap.png}
  \caption{Electrodermal activity (EDA)}
  \label{fig:eda_estimate_bs}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/acc_coef_joint_bootstrap.png}
  \caption{Activity Index (AI)
}  \label{fig:acc_estimate_bs}
\end{subfigure}
\caption{$\beta (t)$ for ACC and EDA with 95\% CI; solid line is point estimate for the missing data analysis, while highlighted region are the boostrap and MI based pointwise 95\% confidence intervals.}
\label{fig:edacc_estimate_bs}
\end{figure}
